### 2008-12-17 talk/ecoop2009/tlc.tex
show an example of tlc assembler, and propose a higher level syntax to show more complex examples

\anto{should we try to invent a syntax for TLC and provide some examples?}
\cfbolz{we should provide an example with the assembler syntax}

>>>>

\subsection{TLC examples}

As we said above, TLC exists only at bytecode level; to ease the development
of TLC programs, we wrote an assembler that generates TLC bytecode. The
following example shows a simple program that computes the absolute value of
the given integer:

\begin{lstlisting}
main:             # stack: []
    PUSHARG       #        [n]
    PUSH 0        #        [n, 0]
    LT            #        [n<0]
    BR_COND neg

pos:              #        []
    PUSHARG       #        [n]
    RETURN

neg:
    PUSH 0        #        [0]
    PUSHARG       #        [0,n]
    SUB           #        [-n]
    RETURN
\end{lstlisting}

Since reading TLC programs at bytecode level is hard, in this paper we will
use an invented Python-like syntax to describe examples, even if we need to
remind that the actual programs are written in the assembler language showed
above. The following listing shows the same example as above written in the
Python-like syntax:

\begin{lstlisting}
def main(n):
    if n<0:
        return -n
    return n
\end{lstlisting}
